---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
title: A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes  
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::pdf_document2:
      toc: false
      number_sections: false
##    md_document: default
##    bookdown::word_document2:
##      toc: false
##      number_sections: false
##      reference_docx: "reference.docx"
---

## Trial registration
This pilot study was registered with ClinicalTrials.gov (reg. no NCT05417243). 

## Corresponding author
Martin Gerdin Wärnberg (MGW)  

Department of Global Public Health  
Karolinska Institutet  
171 77 Stockholm  
Sweden  

martin.gerdin@ki.se  
+46 708 53 95 98 (mobile)  

## Authors


## Contributors

Trauma life support Effectiveness Research Network (TERN) collaborators: 

##### Martin Gerdin Wärnberg (MGW)
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.  

Function Perioperative Medicine and Intensive Care, Karolinska University Hospital, Solna, Sweden.

##### Johanna Berg (JB)
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.  

Emergency Medicine, Department of Internal and Emergency Medicine, Skåne University Hospital, Malmö, Sweden.

##### Prashant Bhandarkar (PB)
WHO collaboration Centre for Research in Surgical Care Delivery in LMIC, Mumbai, India.

##### Anirban Chatterjee (AC)
Department of Orthopaedic Sciences, Medica Superspecialty Hospital, Kolkata, India.

##### Shamita Chatterjee (SC)
Department of Surgery, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Chintamani (C)
Department of Surgery, Vardhman Mahavir Medical College and Safdarjung Hospital, New Delhi, India.

##### Li Felländer-Tsai (LFT)
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.  

Department of Reconstructive Orthopedics, Karolinska University Hospital, Stockholm, Sweden.

##### Anita Gadgil (AG)
WHO collaboration Centre for Research in Surgical Care Delivery in LMIC, Mumbai, India.

##### Geeta Ghag (GG)
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

##### Marie Hasselberg (MH)
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

##### Catherine Juillard (CJ)
Division of General Surgery, Department of Surgery, David Geffen School of Medicine at UCLA, Los Angeles, California, United States of America.

##### Monty Khajanchi (MK)
WHO Collaboration Centre for Research in Surgical Care Delivery in LMIC, Mumbai, India.  

Seth G. S. Medical College and K.E.M. Hospital, Mumbai, India.

##### Deepa Kizhakke Veetil (DKV)
Department of Surgery, Manipal Hospital, Dwarka, New Delhi.

##### Vineet Kumar (VK)
Department of Surgery, Lokmanya Tilak Municipal Medical College and General Hospital, Mumbai, India.

##### Debabrata Kundu (DK)
Department of Surgery, Medical College Kolkata, Kolkata, India. 

##### Anurag Mishra (AM)
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Priti Patil (PP)
WHO collaboration Centre for Research in Surgical Care Delivery in LMIC, Mumbai, India.

##### Nobhojit Roy (NR)
WHO Collaborating Center for Research on Surgical Care Delivery in LMICs, BARC Hospital, HBNI University, Mumbai, India.  

Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

##### Amit Roy (AR)
Department of Surgery, Sir Nil Ratan Sircar Medical College & Hospital, Kolkata, India.

##### Siddarth David (SD)
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.  

Doctors For You, Mumbai, India.

##### Rajdeep Singh (RS)
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Harris Solomon (HS)
Department of Cultural Anthropology and the Duke Global Health Institute, Duke University, Durham, USA.

##### Kapil Dev Soni (KDS)
Critical and Intensive Care, JPN Apex Trauma Center, All India Institute of Medical Sciences, New Delhi, India.

##### Lovisa Strömmer (LS)
Division of Surgery, Department of Clinical Science, Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.  

Department of Surgery, Capio St Göran Hospital, Stockholm, Sweden.

##### Megha Tandon (MT)
Department of Surgery, Vardhman Mahavir Medical College and Safdarjung Hospital, New Delhi, India.

## Keywords
Trauma management, Accident and emergency medicine, Education and training.

## Word Count
<!-- 4494 -->

## Role of study sponsor and funders
The funding sources had no role in the design of this study and will not
have any role during its execution, analyses, interpretation of the
data, or decision to submit results.

\newpage

<!-- Source main code to make global objects available in the text -->
```{r source, echo = FALSE, include = FALSE}
source("main.R")
```

# Abstract

**Introduction** Several trauma life support programs aim to improve trauma outcomes but there is no evidence from controlled trials to show the effect of these programs on patient outcomes. We conducted a pilot study to assess the feasibility of conducting a cluster randomised controlled trial comparing the effect of Advanced Trauma Life Support (ATLS) and Primary Trauma Care (PTC) with standard care on patient outcomes. **Methods and analysis** We piloted a pragmatic three-armed parallel, cluster randomised, controlled trial in India, where neither of these programs are routinely taught. We recruited tertiary hospitals and included trauma patients and residents managing these patients. Two hospitals were randomised to ATLS, two to PTC, and three to standard care. The primary outcome was all cause mortality at 30 days from the time of arrival to the emergency department. We conducted community consultations in parallel with the pilot trial. **Ethics and dissemination** We obtained ethical approval from all participating centres. **Results** Between `r start.date` and `r end.date` we included `r n.patients` patients and `r n.residents` residents from `r n.centres` centres. The patient recruitment rate was X and the resident recruitment rate was X. The loss to follow up rate was X. The all-cause 30 day mortality was X in the ATLS arm, X in the PTC arm, and X in the standard care arm. **Conclusions** Conducting a full-scale cluster randomised controlled trial comparing the effects of ATLS, PTC, and standard care on patient outcomes should be feasible after incorporating key lessons from this pilot. 

\newpage

# Article Summary

Strengths and limitations of this study:

- Cluster randomized controlled trial comparing the effect of ATLS, PTC and standard care on patient and provider outcomes.
- Prospective data collection with direct observations by dedicated project officers.
- Participating centers' heterogeneity may affect the study estimates and bias the results.

\newpage

# Introduction

Trauma, defined as the clinical entity composed of physical injury and
the body's associated response, causes 4.5 millions deaths every year
[@Naghavi2017]. Almost 10% of the global burden of disease is due
to trauma and trauma is the top contributor to the burden of disease in
children and adults aged 10 to 49 years [@Vos2020].

Trauma care is time sensitive and early management of life or limb
threatening conditions is crucial. Several trauma life support training
programs have been developed to improve the early management of patients
as they arrive at hospital by providing a structured framework to
assessment and treatment [@Mohammad2013; @Jayaraman2014;
@Kadhum2020].

The proprietary Advanced Trauma Life Support (ATLS) is the most
established trauma life support training program and more than one
million doctors in over 80 countries have been trained in the program
[@acsAtls2018]. Uptake in low- and middle income countries (LMIC)
has been slow, potentially due to high costs [@Kadhum2020].

The free Primary Trauma Care (PTC) program is the most widely spread
alternative program. The goal of PTC is to improve trauma care in LMIC
[@ptcfPtc2018]. Like ATLS, doctors in over 80 countries have been
trained in PTC, and the program has been endorsed by the World Health
Organization (WHO), among other international organizations
including several professional societies [@ptcfPtc2018].

Despite the widespread use of these training programs there are no
controlled trials showing that they impact patient outcomes
[@Mohammad2013; @Jayaraman2014; @Kadhum2020]. A systematic review
report that hospital trauma life support training is associated with a
reduction in patient mortality, based on studies that were either
observational or quasi-experimental without a control group
[@Jin2021].<!-- Note that some of the studies that Jin include state
that there was no effect of ATLS -->

We will perform a pilot study that aims to assess the feasibility of
conducting a cluster randomised controlled trial comparing ATLS and
PTC with standard care. Recent methodological guidelines indicate that
the design of efficient cluster randomised controlled trials requires
data on probable or target effect sizes, proportion of participants
with the outcome (if binary), and the intracluster correlation
coefficient [@Hemming2017]. The objectives of this pilot study will be
to:

- Estimate probable effect sizes on patient outcomes associated with
  ATLS and PTC compared with standard care, estimate the proportion of
  participants with the outcome (if binary), and estimate the
  intracluster correlation coefficient, as a basis for future sample
  size calculations.
  
- Assess the feasibility of recruiting participants and collecting
  data on primary and secondary outcomes, such as mortality,
  in-hospital complications, length of stay, and quality of life.

- Assess how the effect sizes and directions of these effects of ATLS
  and PTC may differ across clinically important subgroups.

# Methods

## Trial Design
This study will pilot a pragmatic three-armed parallel, cluster
randomised, controlled trial. There will be two intervention arms,
ATLS and PTC training, and one control arm, standard care. We will
collect data for four months in all three arms, first during a one
month observation phase and then during a three month intervention
phase (or continued observation in the control arm). This design will
allow us to assess outcomes both as final values and as change from
baseline. Our study is a pilot study because its objectives involves
estimating quantities, such as the probable effect sizes, proportion
of participants with the outcome (if binary), and the intracluster
correlation coefficient, needed for the sample size calculations of a
full-scale trial [@Hemming2017]. The full-scale trial will be planned
regardless of the effect-sizes identified in this pilot
study. This pilot study will also establish how many
participants that can be enrolled, as well as likely drop out rates,
and the feasibility of collecting primary and secondary outcomes.

## Study Setting
We conducted this pilot in seven Indian tertiary hospitals, where
neither ATLS, PTC, nor any other trauma life support training program
is routinely taught. India is the world's second most populous country
and has 20% of the world's trauma deaths. The trauma system is still
developing, with limited prehospital care, and the in hospital trauma
mortality as well as the proportion of preventable deaths remain
high. Lack of standard trauma training for healthcare providers,
limited hospital resources, inadequate processes of care, overcrowding
emergency departments - are some of the factors that contribute to the
high mortality and morbidity. During recent years efforts have been
made to improve hospital trauma care, through capacity building for
trained trauma care providers, augmenting facilities, and developing
care protocols within the hospitals. We will conduct this trial in
India because training providers in a trauma life support program is
not yet the standard. 

The seven hospitals were King Edward Memorial Seth G. S. Medical
College and K.E.M. Hospital, Mumbai; Lokmanya Tilak Municipal Medical
College and General Hospital, Mumbai; HBT Medical College And Dr. R N
Cooper Municipal General Hospital, Mumbai; Medica Superspecialty
Hospital, Kolkata; Medical College Kolkata, Kolkata; Sir Nil Ratan
Sircar Medical College & Hospital, Kolkata; Postgraduate Institute of
Medical Education & Research, Chandigarh.

## Eligibility Criteria for Participants and Clusters
There will be two groups of participants: patients and resident
doctors.

### Patient Participants
Adults (15 years or older) who present to the emergency department at
participating hospitals with a history of trauma. History of trauma is
here defined as having any of the external causes of morbidity and
mortality listed in block V01-Y36, chapter XX of the International
Classification of Disease version 10 (ICD-10) codebook as reason for
presenting. We will explore intervention effects across the following
clinical subgroups: men, women, blunt multisystem trauma, penetrating
trauma, shock, severe traumatic brain injury, and elderly, as defined by
Hornor et al [@Hornor2018]. The consent form for patients are available
as Supplemental Material 1.

### Resident Doctor Participants
Resident doctors doing their speciality training in surgery (in India
it is very rare to have emergency medicine managing trauma patients in
the emergency department, why we decide to focus on surgical units in
this pilot), who manage trauma patients in the emergency department,
and who are expected to remain in the participating hospitals for at
least one year. To facilitate administration each surgical department
is divided into units, which manages the out patient department,
emergency department, operating rooms etc on different days each
week. One or two, out of typically six, units'
residents will be selected from each hospital. One unit consists of at
least three faculty and three to twelve residents.

To be eligible, units should have a maximum of 25% of the doctors
trained in either ATLS, PTC, or similar training programs before the
start of the pilot (hospitals that have so far agreed to participate
have no or single current residents trained in any program). Those
residents who have received training in the last five years will be
considered as trained. The figure of 25% was decided through consensus
in the research team, to balance feasibility and contamination of
results. We will select the units by conducting a prior survey to
ascertain this criteria. Consent will be sought from the residents in
each of the intervention groups before they undergo the ATLS or PTC
training. The consent form for residents are available as
Supplemental Material 2. We will not ask
for consent from residents at the units in the control hospitals as
their practice will not be affected by this pilot and we will not
collect any personal identifiable data on them. This is in line with
ethical regulations in the study setting.

### Clusters
Indian tertiary care hospitals that admit 400-800 adult patients with
trauma each year. We randomise on the cluster (hospital) level to avoid
contamination between intervention and control arms. To be eligible for
inclusion hospitals have to provide the following services round the
clock: operation theatres, X-ray, CT, and ultrasound facilities, and
blood bank. In addition the baseline admission rate should be more than
35 adult patients with major trauma per month.

## Interventions
In each intervention arm one or two units', out of typically
six, residents per hospital providing
emergency care to trauma patients will be trained in either ATLS or
PTC. For the purpose of this pilot study, we will target to train a
minimum of 75% of residents in each unit. If residents drop out or
change units after training but before data collection is completed we
will conduct additional training if needed to meet the 75% criterion.
We will not train the units' faculty, as they are typically not
involved in the initial management of trauma patients.

The ATLS training will be conducted in the nearest ATLS certified
training centre in India according to the standard ATLS curriculum
[@acsAtls2018]. The PTC training will be arranged in hospitals
randomized to the PTC arm, according to the standard PTC curriculum
[@ptcfPtc2018]. These courses will be conducted over a period of
2.5 to 3 days. The residents certified "pass" will be considered as
trained in respective courses.

The control group provides standard care with no intervention.

### Modifications
Both ATLS and PTC are standard training programs with fixed curricula
[@acsAtls2018; @ptcfPtc2018]. We will not modify the
delivery or content of these programs during this pilot.

### Adherence
The intervention is the training in either ATLS or PTC. Participants are
required to adhere to, i.e. participate in, the training, to be eligible
for passing. We will not consider adherence to training contents during
care delivery as adherence to the trial intervention, but rather as a
provider level outcome.

### Concomitant Care

#### Baseline Training
The care provided by all participating hospitals at baseline is based on
the training curriculum formulated by The National Medical Council of
India for post graduation in General Surgery
[@mciMsSurgery2019]. Regarding trauma, these guidelines state
that the student should:

a.  Have knowledge about response to trauma; burns: causes, prevention
    and management; wounds of scalp and its management; recognition,
    diagnosis and monitoring of patients with head injury, Glasgow coma
    scale.
b.  Be able to provide and coordinate emergency resuscitative measures
    in acute surgical situations including trauma.
c.  Choose, perform and interpret appropriate imaging in trauma -
    ultrasound Focused Abdominal Sonography in Trauma (FAST).
d.  Undergo advanced trauma and cardiac life support course (certified)
    before appearing in final examination.
e.  Undergo clinical posting in emergency and trauma.
f.  Present or discuss cases of blunt abdominal trauma.

Although training in an advanced trauma life support course is part of
the curriculum it is optional and not doing this training does not
result in failure to obtain post graduation completion.

#### Standard of Care
At most medical colleges in India trauma patients present to the
emergency department where they are assessed by a doctor and referred
to the surgical bay for further management. In the surgical bay a
second or third year general surgery resident sees all the major
trauma and provide the initial care, including
initiating treatment and investigations.  This resident informs the
consultant on call who is generally an Assistant Professor. Most
procedures like intercostal drainage, open wound suturing, intubation
etc. would be done in the surgical resuscitation area, by the surgical
resident.

Compared to other settings where a trauma team approach is adopted,
nurses and other healthcare professionals are involved to a limited
extent during the initial management. Their roles include assisting
during intubation and other bedside procedures, charting the vitals
(not recording) and giving injections. They also accompany the
resident during transfers of serious
patients.

After completing the assessment and starting initial resuscitation, the
resident decides to send the patient for imaging (X-rays/FAST/CT-scan)
or to the operation room in consultation with or after assessment by the
on-call consultant. A portable X-ray and an ultrasonography machine to
conduct FAST may or may not be available in the surgical bay. The
patients who are operated, managed conservatively, not intubated, or
with minor trauma will be sent to the surgical ward. Those who need
increased monitoring or mechanical ventilation remain in the surgical
bay or in the intensive care unit (ICU) depending on the availability of
ICU beds. The further treatment continues in the respective ward or ICU
and patients are finally discharged from the ward.

## Outcomes
Our pilot study include both participant and feasibility
outcomes. Prior to deciding on these participant outcomes we searched
the Core Outcome Measures in Effectiveness Trials (COMET) Initiative's
database but were unable to identify appropriate core outcome sets for
our populations of participants.

The primary participant outcome will be all cause mortality within 30
days from the time of arrival to the emergency department. The
primary outcome and most secondary outcome will be assessed and
compared both as final values and as change from
baseline. All outcomes that pertain to the
individual participant level are detailed in Supplemental Material
3. We decided to include a large number of outcomes,
including some more exploratory, so that we can test their feasibility
and relevance. We may remove secondary participant outcomes during the
course of the pilot study, if they prove to be too difficult to
collect. If we remove outcomes we will document the reasons for doing
so.

We will also assess the following feasibility outcomes, which pertain
both to overall study population as well as to the individual cluster
level:

- Recruitment rate. For both patients and residents this will equal
  the proportion of participants enrolled, out of the total number of
  eligible participants, over the course of the pilot study.
- Lost to follow up rate. This will apply only to patients and equal
  the proportion of patients that do not complete 30 day follow up,
  out of all enrolled patients, over the course of the pilot study.
- Pass rate. This will apply only to residents in the intervention
  arms and equal the proportion of residents that pass the training
  programme, out of the total number of trained residents, over the
  course of the pilot study.
- Missing data rate. This will apply to each outcome and variable and
  equal the proportion of missing data, over the course of the pilot
  study.
- Differences in distributions of observed and extracted data. This
  will apply to each outcome and variable and will compare the
  distributions of data collected by observations versus extracted
  from hospital records. For quantitative variables this will be the
  difference in means, standard deviations, medians, interquartile
  ranges, and ranges. For qualitative variables this will be the
  differences in absolute counts and percentages, across categories.

## Participant Timeline

### Patients
Patients will be screened for eligibility as they arrive at the
emergency department. Eligible patients will be approached in the
emergency department to consent to follow up, if they are
conscious. If they are unconscious a patient representative will be
approached to consent to follow up. Once the patient is conscious we
will approach the patient to affirm the patient representative's
consent. We will follow up patients at discharge, at 24 hours after
arrival at the emergency department, and at 30 days after arrival at
the emergency department.

### Residents
Surgical units will be screened for eligibility once hospitals confirm
their participation. All residents in eligible units will be approached
to consent to training if their hospital is randomised to either of the
intervention arms. Training will be conducted as soon as possible after
the study starts. Resident participants will be followed up 30 days
after training, if they are in the intervention arms, or 30 days after
the study started, if they are in the control arm.

## Sample size
Given budget and time constraints, including the rotation of surgical
units in Indian hospitals (which often happen on a six months basis)
the feasible data collection period is four months. Each of the
surgical units see 2-4 trauma patients per week. If we select a
minimum of one unit per hospital then each hospital will enrol 8-16
patients per month and 32-64 patients during the four months of this
pilot. With a 20% attrition rate we expect each hospital to enrol
26-51 patients, coming to a total sample size of between 156 and 306
patients for this pilot study.

## Recruitment
To ensure adequate recruitment we only approach hospitals with trauma
volumes high enough to allow us to reach the sample size goals detailed
above. Patients will be enrolled by a dedicated project officer as they
arrive at the emergency department. The recruitment period will be three
months. Recruitment will be monitored weekly through online conferences.
No financial or non-financial incentives will be provided to trial
investigators or participants for enrolment.

## Allocation

### Sequence generation
We used simple randomisation to allocate sites to trial arms. We
prepared seven sealed envelopes from which one representative from
each pilot site selected one in a common meeting on March 7, 2022
[^dev1]<!-- Meeting notes ../meetings/20220307/ -->. The content of
the envelopes dictated what trial arm (ATLS, PTC, or standard care)
each hospital was allocated to. There were two hospitals in each of
the intervention arms and three hospitals in the control arm.

[^dev1]: Initially the plan was to enroll six hospitals (clusters) but
    we ended up enrolling seven.

### Concealment Mechanism
We did not conceal the sequence.

### Implementation
The random allocation sequence was generated by MGW. Clusters were
enrolled by the project's core team, who also enrolled
clusters. Patient participants will be included if they present during
the project officers shift. Resident participants are enrolled if they
are in the units selected for training. We will use simple random
sampling to select units if there are more than two eligible units in
a hospital. For patient participants consent for follow up is sought
after randomisation from patients or patient relatives as
appropriate. For resident participants consent is sought before
randomisation. If residents in a unit decline to participate, so that
the target of training 75% of residents in a given unit cannot be met,
another unit will be selected for participation.

## Blinding
It will not be possible to blind investigators or participants to
interventions. We will not blind the data analysts during this pilot,
but we plan to blind the data analysts during the full-scale
trial.

## Data Collection
Data collection will start one month before the training is delivered,
to establish a baseline. A variability of three months of the date when
data collection is started between hospitals will be accepted. Each
participating hospital will have a dedicated project officer to collect
data. The project officers will have a masters in a health science field
and should have experience in data collection.

Because participating residents are assigned designated days for trauma
care for a period of 6 months, data will be collected during those
particular days and shifts when these trained doctors are in the
emergency department. The project officers will collect data both by
observing the care delivered and by interviewing the participants, and
by extracting data from hospital records.

Data collection will continue for a minimum of three months after
training. The research officers will collect data of all patients, who
present with trauma in the surgical bay during their duty hours. Those
patients who are admitted will be followed up for complications and
other in-hospital outcome measures, for example length of stay. Patients
who are not admitted will be followed up telephonically for mortality
outcomes and quality of life outcomes. The follow up period will be 30
days. The project officers will make at most three attempts to reach a
participant or participant representative telephonically, after which
the data will be recorded as missing.

The project officer will administer the study information and informed
consent (consent will only be sought for data collection including
follow up) to the patient, or the patient's representative as
appropriate, once the patient is stabilised. They will continue to
collect data once they have received the consent.

Details of data of those patients/relatives not willing to give consent
will be removed from the analysis. The number of patients who opt out
from data collection will be collected, as well as limited data on their
age and sex. Patients will be followed up in the ward regularly for the
various outcome variables. They will also be followed up telephonically
after they have been discharged.

## Variables
The project officers will collect data on demographics, time of injury
to arrival at the participating hospital, time to recording vital
signs, vital signs, and times to and management details including
imaging and surgery. Details of any injury sustained will be collected
and coded using ICD 10 and the Abbreviated Injury Scale (AIS). For ICD
10 coders will undergo the WHO online ICD 10 training module and for
AIS they will be accredited. Based on AIS we will calculate the Injury
Severity Score (ISS) and the New ISS (NISS). Supplemental Material 4
contains a full variable list, with definitions.

## Patient and public involvement
In this study, we will conduct community consultations to collect
inputs from patients, their caregivers, patient groups, and resident
doctors to be used in the selection of outcome measures and
implementation of the full-scale trial; following the Guidance for
Reporting Involvement of Patients and the Public (GRIIPS 2)
[@Staniszewska2017].

During the pilot study, interviews will be conducted with
post-discharge trauma patients and their caregivers to identify
outcomes most relevant to them. These patients will be identified
through the medical registers of the participating hospitals,
contacted through telephone, and after receiving their consent be
interviewed as per their convenience. Their consent form is available
as Supplemental Material 5.  Additionally, members from non-government
organizations working with trauma patients and the hospital Social
Service Section will also be contacted for their views on contextual
patient-centred outcomes for trauma patients. Their consent form is
available as Supplemental Material 6. For feasibility, these
interviews will be held in each of the cities where the participating
centres are located. The commonest patient-centred outcomes reported
across all the locations will be incorporated into the evaluation of
the effects of the different training programs and standardized care
on patient outcomes.

Similarly, the inputs of resident doctor participants at each
participating centre will be collected during the pilot study. A
discussion and periodic surveys will be conducted to document any
challenges or suggestions they may have in the scheduling or
implementation of the training programs. These inputs will be
incorporated in the final study.

A summary of the findings of the study as well as their inputs will be
shared with those who participated in the interviews and surveys. A
meeting will be held with the patient participants, at each city, where
the changes in the measured patient-centered outcomes would be presented
to them. Another meeting will be held with the resident doctors at each
hospital to present the confidence of the residents after being trained.
Any suggestions and reflections from the participants during the
meetings will be used as inputs for planning the final study.

## Data management
We will supply an online data collection tool, accessible only over a
virtual private network (VPN), for each participating hospital to upload
pseudonymised data to secure servers. Data validation techniques like
restricted values or values of a specific range will be used to avoid
ambiguous data entries and ensure the validity of the data. Ambiguous
responses, data errors, if any, will be resolved after discussion with
the core team during weekly meetings. An instruction manual or codebook
for data variables will be prepared to ensure consistency in data entry.
This manual will be referred to during the project data collection and
variable descriptions are visible for each variable in the online data
collection tool. Pseudonymised data will be stored at the centralised
server. The data will be accessible by the project's principal
investigator or by delegation of the project principal investigator
only.

## Data monitoring
Weekly meetings with the core team and project officers will take
place and for this meeting a data status report will be automatically
generated highlighting missing data and number of patients awaiting
followup. We conducted an interim analysis on October 12, 2022, and
decided to complete the study as participants were consenting to be
included in the study and key variables including mortality outcomes
could be collected. No outcomes were dropped. We did not use a data
monitoring committee in the pilot study due to its limited scope.

## Statistical Methods
We will analyse all pilot data using descriptive
statistics. Quantitative variables will be summarised as mean +/-
standard deviation, median, interquartile range and range. Qualitative
variables will be presented as absolute numbers and
percentages. Feasibility outcomes will be summarised both on the
overall sample level as well as on the individual cluster level. We
will use an empty generalised linear mixed model<!-- see [@Sommet2017]
--> to estimate the intracluster correlation coefficient.

We will compare participant outcomes in three combinations of trial
arms: ATLS versus PTC, ATLS versus standard care, and PTC versus
standard care. In each combination we will compare both differences in
final values and differences in change from baseline. For example, for
the primary participant outcome of all cause mortality within 30 days
from the time of arrival to the emergency department, comparing ATLS
versus PTC, we will compare both the difference in mortality between
the ATLS and PTC arms as well as the difference in the change from
baseline in mortality between the ATLS and PTC arms.

For the intervention arms the change from baseline will be calculated
as the difference between the one month period of data collection
before the training was undertaken and the three month period after
the training. For the control arm the data collection period will be
four months and the difference from baseline will be calculated as the
difference between the first one month and the following three months.

Within each combination of trial arms we will conduct subgroup
analyses of men, women, blunt multisystem trauma, penetrating trauma,
shock, severe traumatic brain injury, and elderly. Table S7.1 in
Supplemental Material 7 shows which outcomes will be assessed in which
subgroups, decided through consensus in the research team. We will
further compare the results of all subgroups with the results in the
whole cohort, and compare the results in the female subgroup with the
male subgroup, and the results in the blunt multisystem trauma
subgroup with the penetrating trauma subgroup. We are aware that the
numbers in some of these subgroups are likely to be small, but we
include them to help guide the formulation of the statistical analysis
plan for the full-scale trial.

We will calculate both absolute and relative differences for each
comparison, along with 75, 85, and 95% confidence intervals. We will
use an empirical bootstrap procedure with 1000 draws to estimate these
confidence intervals. We will not perform any formal hypothesis tests
during the analysis of this pilot's data [@Lee2014]. We will also
compare the data collected through observations and interviews with
the data collected from hospital records, to assess the feasibility of
collecting data from hospital records in the full-scale trial.

## Ethics and Dissemination
We were granted research ethics approval from each participating
hospital. The approval numbers were IEC(II)/OUT/134/2022 for King
Edward Memorial Seth G. S. Medical College and K.E.M. Hospital,
Mumbai; IEC/214/22 for Lokmanya Tilak Municipal Medical College and
General Hospital, Mumbai; HBTMC/266/SURGERY for HBT Medical College
And Dr. R N Cooper Municipal General Hospital, Mumbai;
CREC/2022/FEB/1(ii) for Medica Superspecialty Hospital, Kolkata;
Medical College Kolkata, Kolkata; NRSmC/IEC/93/2021 for Sir Nil Ratan
Sircar Medical College & Hospital, Kolkata; and PGI/IEC/2022/000/003
for Postgraduate Institute of Medical Education & Research,
Chandigarh.

The protocol was published in BMJ Open [@GerdinWärnberg2022] and was
registered with ClinicalTrials.gov (reg. no NCT05417243). Amendments
to the protocol after publication were determined by the core research
group and updated on ClinicalTrials.gov.

The final anonymized dataset and code for analysis are released
publicly. Authorship follows the International Committee of
Medical Journal Editors (ICMJE) guidelines.

# Results

**Note that participating centres are randomly assigned to the
different arms every time this manuscript is compiled**

Between `r start.date` and `r end.date`, we enrolled `r n.patients`
trauma patients from `r n.centres` participating centres. The ATLS arm
enrolled `r n.atls` patients, the PTC arm `r n.ptc` patients, and the
standard care arm `r n.control` patients. We trained a total of 
`r n.residents` residents, `r n.atls.residents` in ATLS, and 
`r n.ptc.residents` in PTC. 

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table 
\@ref(tab:sample-characteristics). Overall, the
number of females were X (X%), the median age was X (IQR X), and the
median ISS was X (IQR X). A total of X (X%) patients had the primary
outcome of mortality at 30 days after arrival to the emergency
department.

```{r sample-characteristics, echo = FALSE, results = "asis"}
create_descriptive_table(table.data,
                         strata = "patinfo/pt_gender",
                         caption = "Patient sample characteristics")
```

## Patient Participant Outcomes
In the post training period, a total of X (X%) patients in the ATLS
arm had the primary outcome, compared to X (X%) patients in the PTC
arm, and X (X%) patients in the standard care arm. The differences
between the arms were X (95% CI X - X) between the ATLS and PTC arms,
X (95% CI X - X) between the ATLS and standard care arms, and X (95%
CI X - X) between the PTC and standard care arms. The change from
baseline for the primary outcome was X in the ATLS arm, X in the PTC
arm, and X in the standard care arm. The differences between changes
from baseline were X (95% CI X - X) between the ATLS and PTC arms, X
(95% CI X - X) between the ATLS and standard care arms, and X (95% CI
X - X) between the PTC and standard care arms. Table X shows
differences in the primary outcome between trial arms with 75, 85, and
95% CIs. Differences in secondary outcomes between trial arms and
subgroups are available as Supplementary material X.

## Resident Participant Outcomes
A total of X residents were trained during this pilot. Overall their
confidence in managing trauma patients was X (IQR X - X) on a 10 point
Likert scale with 10 being most confident. In the post training
period, the confidence in the ATLS arm was X (IQR X - X), compared to
X (IQR X - X) in the PTC arm, and X (IQR X - X) in the standard care
arm. 

## Feasibility Outcomes
Out of X potentially eligible patients, X (X%) patients were enrolled
in the study. Out of X potentially eligible residents, X (X%) were
enrolled in the study. The loss to follow up rate was X, with X out of
X patients not completing 30 day follow up. Among residents the pass
rate, after two attempts, was X (X%). The missing data rate ranged
from X to X, with details per variable and outcome in Table X. The
differences in distributions between observed and extracted data, for
variables that were collected through observation or interview, are
shown in Table X.

## Community Consultations
The results of interviews with patients, caregivers and social workers
will be published separately. Residents felt that...

# Discussion
We show that conducting a cluster randomized controlled trial
comparing ATLS with PTC and standard care is feasible in this setting
provided that there are dedicated project officers to enrol
participants, collect data, and follow up participants. Missing data
rates were low for the primary outcome and many secondary outcomes, as
well as for key variables. Some variables had very high missing data
rates and may not be feasible to include in a full-scale trial.

<!-- Should we include dependency at discharge, for example using the
Modified Oxford Handicap Scale used in @Roberts2013?-->

We found that the ATLS arm had lower 30-day mortality compared to the
PTC and standard care arms.

We found that the PTC arm had lower 30-day mortality compared to the
ATLS and standard care arms.

We found that the standard care arm had lower 30-day mortality
compared to the ATLS and PTC arms.

We found that 30-day mortality was similar in the ATLS and PTC arms
but lower than the standard care arm.

We found that 30-day mortality was similar in the ATLS and standard
care arms but lower than the PTC arm.

We found that 30-day mortality was similar in the PTC and standard
care arms but lower than the ATLS arm.

The primary patient participant outcome, all-cause 30-day mortality,
was missing in X% of patients. This may appear high, especially
compared to for example the CRASH-2 and REACT-2 trials, which report
missing primary outcome in less than 0.01% of patients [@Roberts2013;
@Sierink2016]. Like many other trauma trials, both CRASH-2 and REACT-2
used in-hospital mortality as their primary outcome measure, whereas
we attempted to follow up patients after discharge. The missing data
rate for in-hospital mortality was only X%, comparable to previous
trials.

<!-- Consider discussing non-inferiority vs superiority. -->

During the course of this pilot we deviated from the protocol in
multiple ways, and provide a detailed list as Supplementary
material. Some key limitations of this pilot and therefore lessons to
be learned and factored into the design of the full-scale trial
include the lower than expected enrolment rates of some centres,
centre specific management routines, and difficulties in collecting
data on complications and cause of death. We minimised the impact of
the lower than expected enrolment rates by including a seventh centre,
but on-site observations of patient volumes are likely to be needed
for the full-scale trial. We decided to be pragmatic in selecting
which residents to train and how to structure the data collection
depending on how and by whom patients were initially managed, but this
flexibility will need to be built into the full-scale trial
protocol. Finally, we found that data on complications and cause of
death were hard to identify and therefore the full-scale trial will
need to include longer training of project officers.

Previous studies on the effect of in-hospital trauma life support
training on patient outcomes are observational or quasi-experimental
without a control group, with heterogeneous results
[@Ariyanayagam1992; @CioèPeña2016; @Petroze2014; @VanHeng2008;
@Wang2010]. Studies from Trinidad and Tobago, El Salvador, Rwanda, and
Cambodia found no significant effect on patient mortality after
implementing in-hospital trauma life support training
[@Ariyanayagam1992; @CioèPeña2016; @Petroze2014; @VanHeng2008],
whereas one study from China that included 820 patients found a
significant reduction in mortality, from 20 to 15%, after implementing
ATLS [@Wang2010].

Several controlled trials, including at least two randomized
controlled trials [@Ali1996; @Ali1999], show that ATLS is associated
with improved provider skills [@Mohammad2013]. Observational evidence
indicates that PTC also leads to improved provider skills
[@Kadhum2020]. The missing link is then how, and if, these improved
skills translate into improved patient outcomes. As trauma care
providers we assume, and probably rightly so, that we deliver better
care if we train. The question is then how we should train, especially
considering the costs associated with some of the programs
offered. 

We conclude that a full-scale cluster randomised trial should be
feasible after incorporating the lessons of this pilot, and that this
full-scale trial should, regardless of its outcome, influence how we
train trauma care providers in the future.
 
# Contributorship statement
MGW conceived of the study. AG, AM, CJ, DKV, HS, JB, KDS, LFT, LS, MH,
MGW, MK, NR, PB, PP, RS, SD, and VK contributed to the design of the
study. DKV, KDS, MK, and MGW drafted the first version of the
protocol. AG, HS, and SD drafted the first version of the patient and
public involvement activities. JB and PP drafted the first versions of
the data management sections and wrote the data management plan. PB
and PP drafted the first versions of the statistical analysis
section. AG, AM, CJ, DKV, HS, JB, KDS, LFT, LS, MH, MGW, MK, NR, PB,
PP, RS, SC, SD, and VK contributed to the refinement of the
protocol. AR, AC, C, DK, GG, MK, MT, and VK are representatives of
prospective participating hospitals.

# Competing Interests
Several authors are Advanced Trauma Life Support or Primary Trauma
Care instructors.

# Funding
Doctors for You through grants awarded to Karolinska Institutet by the
Swedish Research Council (grant number 2020-03779) and the Laerdal
Foundation (grant number 2021-0048).

# Data Sharing Statement
The final anonymized dataset and code for analysis will be released publicly.

# Protocol Deviations

## Trial Registration
We intended to also register our trial with Clinical Trials Registry -
India but because of time constrains we had to initiate the study
before registration was finalised, and Clinical Trials Registry -
India only allow prospective registration.

## Number of Participating Centres
We ended up recruiting seven centres instead of six and therefore
assigned two centres each to the intervention arms and three centres
to the control arm.

## Resident Participants
Emergency medicine in addition to surgery.

## Periodic suverys to residents
We did not distribute periodic surveys to the participating residents
but discussed challenges and suggestions that they had regarding the
scheduling or implementation of the training programs.

## Data collection from records
We decided to record data from records only for a subset of patients
to reduce the project officers' workload.

# References
