# 75% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

```



## Outcomes in all patients before training, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients before training, by treatment arm"]]

```



## Outcomes in all patients after training, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients after training, by treatment arm"]]

```



## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

```



## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

```



## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

```



## Absolute and relative differences in outcomes after training, comparing standard care with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

```



## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]

```



# 85% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

```



## Outcomes in all patients before training, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients before training, by treatment arm"]]

```



## Outcomes in all patients after training, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients after training, by treatment arm"]]

```



## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

```



## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

```



## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

```



## Absolute and relative differences in outcomes after training, comparing standard care with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

```



## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]

```



# 95% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

```



## Outcomes in all patients before training, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Outcomes in all patients before training, by treatment arm"]]

```



## Outcomes in all patients after training, by treatment arm

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Outcomes in all patients after training, by treatment arm"]]

```



## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

```



## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

```



## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

```



## Absolute and relative differences in outcomes after training, comparing standard care with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

```



## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

```



## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

```{r, echo = FALSE} 

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]

```


