# 75% confidence level

## overall

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["overall"]]

```



## pre.training

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["pre.training"]]

```



## post.training

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["post.training"]]

```



## absolute.difference

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["absolute.difference"]]

```



## relative.difference

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["relative.difference"]]

```



## Post training outcome Standard care vs. ATLS

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["Post training outcome Standard care vs. ATLS"]]

```



## Post training outcome Standard care vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["Post training outcome Standard care vs. PTC"]]

```



## Post training outcome ATLS vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["Post training outcome ATLS vs. PTC"]]

```



## Change from baseline Standard care vs. ATLS

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["Change from baseline Standard care vs. ATLS"]]

```



## Change from baseline Standard care vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["Change from baseline Standard care vs. PTC"]]

```



## Change from baseline ATLS vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.75"]][["Change from baseline ATLS vs. PTC"]]

```



# 85% confidence level

## overall

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["overall"]]

```



## pre.training

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["pre.training"]]

```



## post.training

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["post.training"]]

```



## absolute.difference

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["absolute.difference"]]

```



## relative.difference

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["relative.difference"]]

```



## Post training outcome Standard care vs. ATLS

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["Post training outcome Standard care vs. ATLS"]]

```



## Post training outcome Standard care vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["Post training outcome Standard care vs. PTC"]]

```



## Post training outcome ATLS vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["Post training outcome ATLS vs. PTC"]]

```



## Change from baseline Standard care vs. ATLS

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["Change from baseline Standard care vs. ATLS"]]

```



## Change from baseline Standard care vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["Change from baseline Standard care vs. PTC"]]

```



## Change from baseline ATLS vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.85"]][["Change from baseline ATLS vs. PTC"]]

```



# 95% confidence level

## overall

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["overall"]]

```



## pre.training

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["pre.training"]]

```



## post.training

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["post.training"]]

```



## absolute.difference

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["absolute.difference"]]

```



## relative.difference

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["relative.difference"]]

```



## Post training outcome Standard care vs. ATLS

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["Post training outcome Standard care vs. ATLS"]]

```



## Post training outcome Standard care vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["Post training outcome Standard care vs. PTC"]]

```



## Post training outcome ATLS vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["Post training outcome ATLS vs. PTC"]]

```



## Change from baseline Standard care vs. ATLS

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["Change from baseline Standard care vs. ATLS"]]

```



## Change from baseline Standard care vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["Change from baseline Standard care vs. PTC"]]

```



## Change from baseline ATLS vs. PTC

```{r, echo = FALSE} 

tables[["ci.level.0.95"]][["Change from baseline ATLS vs. PTC"]]

```


